\chapter{Chapter 1}
\label{chapter:1}

This chapter consists of two sections.

\section{Section 1}
\label{section:1}

What are you trying to achieve in this paragraph and in your whole composition? What is your purpose right here? Do you wish to describe? Do you want to evaluate? Is your goal to narrate? Is your intent to persuade?

\textbf{Table 1. The Adrenergic Receptors}
\begin{table}
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Receptor}   & \textbf{Affinity} \\ \hline
    Alpha-one  & NE>E \\ \hline
    Alpha-two  & NE>E \\ \hline
    Beta-one   & NE=E \\ \hline
    Beta-two   & E>NE \\ \hline
    Beta-three & NE+E \\ \hline
    \end{tabular}
\end{table}

\section{Section 2}
\label{section:2}

Sunset is the time of day when our sky meets the outer space solar winds. There are blue, pink, and purple swirls, spinning and twisting, like clouds of balloons caught in a blender. 

When water collects on a road, a vehicle can hydroplane. \ntiglossaryentry{\textbf{Hydroplaning}}{\textbf{Hydroplaning }--- Condition in which moving tires (automobile or aircraft) are separated from pavement surfaces by steam and/or water or liquid rubber film, resulting in loss of mechanical braking effectiveness.} is a condition in which directional control is partially or totally lost because of water on the roadway. It is caused when the tires lose contact with the road surface and have little or no traction. Braking and steering may not be possible while hydroplaning.

\begin{sidebar}{Sidebar 1}
One of the easiest ways to display complex information is by organizing it visually. Tables are particularly useful for this. Here are three examples of information presented in table form.
\end{sidebar}

The sun moves slowly to hide behind the line of horizon, while the moon races to take its place in prominence atop the night sky. People slow to a crawl, entranced, fully forgetting the deeds that still must be done. There is a coolness, a calmness, when the sun does set.

