\chapter{FAQ}
\label{chapter:FAQ}

\section{System Requirements}
\label{section:System Requirements}

We recommend the following specifications to ensure the highest quality experience while using NextThought:

1Mb/s+ broadband Internet connection for optimal video viewing
A computer with at least 2GB memory and minimum screen resolution of 1024x768
\href{http://get.adobe.com/reader/}{Adobe Reader} or similar PDF reading software

\section{General Features}
\label{section:General_Features}

\textbf{Can everyone see the note I just made?}\\

You control who is able to see your note. To change who your note is shared with or add someone to the note, begin typing a contact, list, or group's name in the sharing field and click on them to share. To remove a person, group, or list, hover over their name in the sharing field, and an "x" will appear. Click the x to remove. If no one is listed in the sharing field, the note will be private and only you can access it.

\chapter{Getting Started}
\label{chapter:Getting_Started}

\section{Book Organization and Navigation}
\label{section:Book_Organization_and_Navigation}

Your homepage displays when you first log in and contains the books required to complete your training. Click on a \textbf{book} to begin.

Your book will open on the first page. Notice at the top of the page are navigational tools: the first icon opens the \textbf{table of contents} and \textbf{search}. Click on it to preview the entire book outline. Click on a chapter, section, or subsection to navigate directly to that content. 